\documentclass{article}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage{graphicx}
\usepackage{pifont}
\usepackage{qtree}
\usepackage{tikz}
\usetikzlibrary{automata,arrows,positioning,calc}
\usepackage{listings}
\usepackage{hyperref}
\newenvironment{scprooftree}[1]%
{\gdef\scalefactor{#1}\begin{center}\proofSkipAmount \leavevmode}%
{\scalebox{\scalefactor}{\DisplayProof}\proofSkipAmount \end{center} }

\begin{document}
\lstset{language=Java}
\author{Jappie Klooster}
\title{Thoughts about cognition}
\maketitle

\section{Introduction}
This will be an introduction to cognitive proccessing
coming from someone who followed
` hbo informatica' as pre study.

In here I will write down the things I think are important.

\section{Research and design}
This chapter will talk about how to set up experiments and how to draw
conclusions from them. It will also discuss what tools are available.
Matlab was also discussed, but considering my background I will not spend
time on this subject.

\subsection{Brains}
The human and monkey brain are rather similiar (in shape mostly).

\subsubsection{Why do we have brains?}
Reproduction is an important factor, there exists animals that consume their
own brain ones they start making their offspring.

\subsection{Common denominator}
All the brains have neurons.

Incoming singals arrive at denrites, and are integrated to trigger an outgoing.
signal (or not) at the axon hillock.
Cell firing action potential is sent down the axon, which is often insulated
with meylin to increase conduction peed, jumping between the nodes of ranvier.

When the action potential arrives at the terminal bouton, neurotransmitters
are realeased to activate the next cell.

\subsubsection{Action potentials}
At the baseline, neuron potential difference between the outside and inside
of the cell is about -70mv. Incoming singals(arrows) cause changes that
make the inside of teh cell more positive. When a treshold is reached a
cascade of events is triggeredthat make the inside of the cell very positive,
very quickly. This discharge is the action potential and starts at the hillock.
It travels trough the axon to the next cell.

So the charge level slowly built until a treshold, and then releases. This
causes chemicals to jump at the terminals. Which is treated as an incoming
singal to the next neuron.

\subsubsection{Neuro transmision}
Neuro transmission is done with neurotranmitters, there are two main
transmitters, Glu, which makes the next cell more likely to fire, its
exictatory. GABA makes the next cell less likely to fire, its inhibitory.

Neurotransmitters (NT) are stored in vesicles. Electrical signal causes
vesicles to bind with the membrane of the terminal and thus release NT
out of the cell into synaptic cleft. NT spread and ome bind to next
cell at particluar locations: receptors. Binding to receptor causes
changes in the cell that may result in it signaling/firing itself.

The synaptic cleft is the gap between the axon terminal and
the dendritic spine.

\paragraph{Receptors} Usually a protein channel. NT can bind to it
and change its shape. When open: Ions can flow trough it and
chagne the electrical potential of the cell (try to excite or
inhibit it).

Many receptors come in the form of `channels'. This is a chanal,
aka potential opening, between the in and outside of the cell.
Depending on how it's folded it may allow ions to pass or not.
Its shape also makes it selecive: Only some ions can pass.

There are many different kinds (Glu, Gaba, dopamine etc).
Sensory receptors repsond to the outside world instead of signals
from other neurons: Light, pressure, taste or smell molucles vibration etc.

Dopamine and serotine are very common. Not main transmitter but important
modulators of activity. Not all recptors are channals. We also have sensory
recptors. They're special and can be very different. Complex molecules bind
to chemical recptors in the nose and on the tongue. Hair cels in the cockle
(ear) respond to vibration of a particular frequency.

\subsection{Sensory systems}
Converting energy from outside the body to neural signals trough: stimulus.
Modification of signal, transduction  or transfer.

Flavour is a multi sensoy phonomon. Olfaction and ustation strong connections
to limbic system. Chemo signalling affects behoviour, perception and emmotions.

Chemical senses appear to have a strong link to social behaviour.

\subsubsection{The pupil}
Allows more or less light to enter the eye. More light usually not a good idea.
Dilation: arousal, Contrsiction: Relaxation.

Sensory aquisition \& rejection: emotrion affects pupil respones.

\subsubsection{Smell}

MHC: Major histocompatibility complex. Genes with product that is part of
immume systems Having more different. Smelling mice and vice versa.

Humans can small differences beteween mouse families only differing in MHC.
mice can recognise human MH-types from urine.


\paragraph{Do we use it?} Contraceptives seem to interfere with natural mate
selection: A big deal because similiar MHC tends to reduce succesfull
pregnacies.
\subsubsection{Transduction}
converts physical (in real world, such as sound or pressure) signals to neural
It can use chemical mechanical both or neither.

\subsubsection{Transfer}
From the transduction, to the brain, or CPU.
%I guess a brain counts as a
%processing unit and its pretty central so, yeah CPU fits fine.

\subsection{Receptive fields}
Description depends on modality. Somatosensory, Auditory, Visual, Gustation.

Pain for example spreads from 1 point to the entire surrounding area, even
if its not affected.

\subsubsection{space}
The relation to space is well maintained in early sensory processing.

\subsubsection{response profiles}
What is the relation between a stimulus and a response?  Its an S curve.
How is the strenth of an external stimulus related to its proccessing?

\subsection{Adoptation}
Sensory responses are not stable over time.

The frequency of output of a snesory cell goes down over time. After
excitiation
the cell becomes more negative, becuase it pushed out all these postive ions
that entered during the spike. In the period just after the spike no positive
ions are allowed in. This makes it harder to reach the threshold for an
action potential.

Neurons adapted to their prefered stimulus are hyperpolarized. Repatitive
presynaptic stimulation depletes a readily releasable vescile pool.
It takes time to refill the readily releasable pool.

\subsection{Simple \& complex signals}
Neurons are used for information processing. They take information from
one or multiple sources and trn it into something else. Usually a more
complex form of information.

\paragraph{But} perception does not coincide with reality. Think of all the
illusions you may have seen on the web.

\subsubsection{Light reaches the retina}
Beofre light reaches the lens it already gets transformed. The cornea
(outside harder part) filters UV-light. Another interseting feature is the
layout. The axons of ganglion cells, which sends onfio to the brain,
are actually in front of the recoptors that decode light.
This already has a profound effect on vision the blindspot.

\subsubsection{Responding to light}
1 type of photo recoptors: rods and cones. They differ in the type of light
they respond to. They prefer different wave lengths. The cones will later
be used to figure out color. The rods are more sensitive to light, and
are used mostly in dark envioronments. They respond to light rather simliarly.
Both are filled with pgiments and this pigment is what gets effected by light.
Photons kind of destroy it.

\subsection{Processing vision}
\subsubsection{Horizontal cells}
It processes it with cirlces and there is some basic logic
going on when the signals leave the eyes (nand gates and such).

\subsubsection{V1}
Processes light and dark paterns, the cells aren't to pickey (always give
of some signal) but some have preference for certain orientations.

\subsubsection{V2}
% A heuristic layer?
Responds to known rules of the visual world. Patterns we are used to seeing.

Receptive fields go from simple and small to progresivley complex and large.

\subsubsection{After V2}
Things become very complex very fast.

\subsection{Scanning techniques}

\subsubsection{MRI}
Magnatic resonanse imaging, fMRI is the same but uses
the diff of 2 images. MRI always uses blood oxygion
levels to get an image.

\paragraph{DPRI}
Same as MRI but measures water instead of oxygian.
This can potantioally image communcation between parts
of the brain. But its a work in progress.

\subsection{EEG}
Measure the activity in the brain, great temporal res,
but bad spatial res.

\paragraph{ECoG}
EEG with open skull. Great temporal and good spatial res.
But its invasive, so there is little opertunity to o this.

\subsubsection{MEG}
Best thing, has high temporal and spatial resolution.
But is very expensive.

\subsubsection{TMS}
The zapping. It does not give an image but it interferes
with brain activity instead by sending and EMP.
% I'm going to stay away from this one.

\paragraph{rTMS} Long term TMS by using repeated zaps.
It may work as an antidrepresant, but drug companys try to fight these 
results.

\subsubsection{Drugs}

You can also use drugs to mess with the brain.

\section{Langauge}
Trying to figure out what langauge is.

\section{Langauge and Context}
In here we will focus on trying to reduce the influence of context or
at least try to explain it.

\end{document}
