\documentclass{article}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage{graphicx}
\usepackage{pifont}
\usepackage{qtree}
\usepackage{tikz}

\newenvironment{scprooftree}[1]%
{\gdef\scalefactor{#1}\begin{center}\proofSkipAmount \leavevmode}%
{\scalebox{\scalefactor}{\DisplayProof}\proofSkipAmount \end{center} }

\begin{document}
\author{Jappie Klooster}
\title{Free asociations}
\maketitle

\section{Thoughts on results}
The first friend I asked didn't took the
test serious (thats why the associations don't make much sense), I'm not
sure if I should remove this data or just keep it.

The personal category was added for words that really don't have any
relation to the other word, this is justified because some poeple might
have a strong memory with a particular word. For example if your best
friend just died and sombody tries to do this test and says friend,
death might be the first response.

Coolocation and coordination are by far the most common responses.

It should be noted that results 3 till 10 are done on my classmates,
so they are biased. Although I don't think it really matters for this
kind of test, because you should say the first thing that comes to mind.
If people want to give a different anwser they're gonna give a different
anwser. Regarldess of training.

\section{Reactions on colecting}
The first 2 participants I asked where some friends of my. I did this trough
Whatsapp. They were both quite curious about why I did it. They were also
interested in the `results'.

I think people often think you are testing them personally rather than
just collecting some data. At least thats how I felt when I got tested in class.
Because of this I think people will try to do extra `their' best.
Or in case of my first friend, just troll it.

The other 8 participants were classmates. So they required a lot less explaining.

\section{Comments on the assignment}
It is rather difficult to find subjects. But once you managed to find the
subject the assignment is quite easy. I'm not sure I did it right but I
think I did.

I think that the assignment small for group work,
giving it a week before the exams isn't great either.
\end{document}
