\documentclass{article}
\begin{document}
\author{Jappie Klooster}
\title{Temporal magick or logic}
\maketitle
\section{Linear temporal magick}

$\phi_1\cup\phi_2$ = $\phi_1$ holds until $\phi_2$ becomes true.
$\Diamond\phi$ = sometimes
$O\phi$ = next time

$M=(S,\sigma, \pi)$ where $S$ is a set of states, $\sigma: N \to S$ is an
infinte seqence of states

\subsection{Semantics}
$\vdots$
$M,\sigma\vDash O\phi \LeftRightArrow M, \sigma^1 \vDash \phi$ next time
$M,\sigma\vDash \Diamond\phi \LeftRightArrow M, \sigma^n \vDash \phi$
invention, there is some time where $\phi$ is gonna hold.

\subsubsection{untill}
if $\phi_2$ holds somewhere it does not mean it holds everywhere after that
point

$\phi_1$ holds until $\phi_2$ holds.

weak untill = where $\phi_1$ holds everywhere because there is no
$\phi_2$, for example $\phi_1^{\bot}$

\section{Branching temproal magick}

Two kinds of formulas, state formulas, path formulas.
Any state formula can also act as a path formula.

\subsection{Models}
serial, any point has a continuation, time never stops.
$S \times S$ = cartesian product of S.

Fullpath is a ninfinite seq of states more or less true the tree.
These are more or less the lines of linear logic.
Fullpaths can start anywhere, not necisarly at the root.

$\sigma_1$ = already a choice of the branch, so no need for no trees.

\section{Combination of BDI}
E = optional
A = inevitable

\section{Operators magick}
$\Diamond\Diamond\phi=\Diamond\phi$
$\Box\Box\phi=\Box\phi$
$\Box\Diamond\phi$=Infenitly often there is a point where $\phi$ holds.
$\Diamond\Box\phi=$Some point in the future $\phi$ will hold indevinitly

\subsection{BDI}
Optionally $\Diamond p$ = there is a choice where p is gonna hold
Optionally $\Box r$= there is a timline where r is gonna hold
Inevitiably $\Diamond s$=  ???
Inevitiably $\Box b$=  b always holds

\section{BDI sementics}
s.t. = such that.

From t1 to t2, the agent has a memory, but he can doubt about the future.
There is the hidden asumption that agents have memory.

success = there exist some period in wehre the even was succesfull

\subsection{Axiom}
written like $GOAL(\alpha) \subset BEL(\alpha)$, but russel notation :s so
$\subset = \to$
$GOAL(\alpha) \to BEL(\alpha)$ = believe-goal compatibility
different from cohon and laveque, $BEL \alpha \to GOAL \alpha$, because
its a different framework, but the reason behind it is the same strangely
enough.

$INTEND(does(e))\to does(e)$ intention leads to action, which is controversial

\subsection{compatibility}
Sinning = ???, something with cutting of branches.

\section{CTD}
\subsection{Axioms}
$done(e) \to BEL(done(e))$,  you're awere that you've done something


\section{Praktical}
The general strategy is to write down what you have to proof and then to
read with help of the definitions.

Don't be sloppy and take an arbitrary M with for all's
\subsction{3.16}
\[\vDash \alpha \Rightarrow \vDash BEL x \alpha\]
Assume $\Vdash \alpha$, so $M,\sigma,v,n\vDash \alpha$ for all $M,\sigma,v,n$(*)
To prove $\vDash BEL x \alpha$, 
	ie $M,\sigma,v,n\vDash BEL x \alpha$ for all $M,\sigma,v,n\vDash$
	ie $M,\sigma,v,n\vDash\alpha$ for all $\sigma'$ with (\sigma,n)B[v(x)]
	\sigma' done by (*).

\subsection{3.26}
	To prove: $M,\sigma,v,n\vDash BEL x \alpha \to Goal x \alpha$ for all 
	$M,\sigma,v,n$.
	ie $M,\sigma,v,n\vDash BEL x \alpha \Rightarrow M,\sigma,v,n\vDash$ Goal
		$x \alpha$ for all $M,\sigma,v,n$
		ie $M,\sigma',v,n\vDash \alpha$ for all $\sigma'$ with $\sigma,n)
		B[v(x)]\sigam'\RIghtarrow M,\sigma'',v,n\vDash \alpha$ for all
		$\sigma''$ with $(\sigma,n)G[v(x)]\sigma''$

		Given:
		$(\sigma,n)G[v(x)]\sigma''\Rightarrow(\sigma,n)B[v(x)]\sigma''$
		$\vdots$

		Take arb $\sigma''$ with $(\sigma,n)G[v(s)]\sigam''$ then also 
		$(\sigma,n)B[v(x)]\sigma''$ so $M,\sigma,v,n\vDash \alpha$
\subsection(3.11)
Proof
\begin{prooftree}
	\AxiomC{}
	\UnaryinfC{}
\[ \vDash \neg LATER(\Diamond p) \neg LATER(\Diamond p) \LeftRightarrow 
\neg(\neg\Diamond p) \Leftrightarrow \neg(\neg\Diamond p \wedge 
\Diamond\Diamond p) \Leftrightarrow \neg(\neg\Diamond p \wedge 
\Diamond p)\]

\end{prooftree}

\subsection{3.13}
\begin{prooftree}
	\AxiomC{$\vDash \Diamond q \wedge BEFORE pq \to \Diamond p$}
	\UnaryInfC{To prove $M,\sigma,v,n\vDash \Diamond q \wedge BEFORE pq \to \Diamond p$ for all $M,\sigma,v,n$}
	\UnaryInfC{Take arbitrary $M,\sigma,v,n$ to prove $M,\sigma,v,n\vDash \vDash \Diamond q \wedge BEFORE pq \to \Diamond p$ for all $M,\sigma,v,n$}
	\Rightlabel{ie}
	\UnaryInfC{To prove if $M,\sigma,v,n\vDash \Diamond q$ and 
	$M,\sigma,v,n\vDash BEFORE pq$ then $M,\sigma,v,n\vDash Diamond p$ for all $M,\sigma,v,n$}
	\UnaryInfC{Supose $M,\sigma,v,n\vDash \vDash \Diamond q$ and 
	$M,\sigma,v,n\vDash BEFORE pq$}
	\Rightlabel{ie}
	\UnaryInfC{Supose $M,\sigma,v,n\vDash \exists x HAPPENS x;q?$ and 
		$M,\sigma,v,n\vDash \exists \forall c (HAPPENS c;q{?}) \to \exists q$ 
	$q\se c \wedge HAPPENS a;p{?}$}
	\Rightlabel{ie}
	\UnaryInfC{Supose $M,\sigma,v,n\vDash \exists x HAPPENS x;q?$ and 
		$M,\sigma,v,n\vDash \exists \forall c (HAPPENS c;q{?}) \to \exists q$ 
	$q\se c \wedge HAPPENS a;p{?}$}
\end{prooftree}

\end{document}
